<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-08 paper-supplementary.Rmd
deleted contribution of hod and moy

@@

group <- f %>% hclust (method = "ward.D") %>% cutree(k=17)
cluster_result <- bind_cols(customer_id = id, group = group)

@@

# contribution of hod

```{r contribution}
# data_validation <- hod %>%  
#   rename("hod" = "distance") %>% 
#   left_join(moy, 
#             by = c("item1", "item2"))%>% 
#   rename("moy" = "distance") %>% 
#   left_join((wkndwday), 
#             by = c("item1", "item2"))%>% 
#   rename("wkndwday" = "distance") %>% 
#   left_join(cluster_result, by = c("item1" = "customer_id")) %>% 
#   rename("group_item1" = "group") %>% 
#   left_join(cluster_result, by = c("item2" = "customer_id")) %>%  
#   rename("group_item2" = "group") %>% 
#   mutate(hod = hod/24, moy = moy/12, wkndwday = wkndwday/2) %>% 
#   filter(!is.na(group_item1)| !is.na(group_item2)) %>% 
#   pivot_longer(3:5,names_to="gran",
#                values_to = "distance")  
#

data_validation_cat <- read_rds(here::here("validation/data_validation_cat_all_cluster.rds"))

# hod_cat <- data_pick %>%
#   dist_gran_cat(gran1 = "hour_day", response = "general_supply_kwh") %>%
#   mutate(gran = "hod")
# 
# moy_cat <- data_pick %>%
#   dist_gran_cat(gran1 = "month_year", response = "general_supply_kwh")%>%
#   mutate(gran = "moy")
# 
# wkndwday_cat <- data_pick %>%
#   dist_gran_cat(gran1 = "wknd_wday", response = "general_supply_kwh")%>%
#   mutate(gran = "wnwd")
# 
# 
# data_validation_cat <- bind_rows(hod_cat, moy_cat, wkndwday_cat) %>%
#   mutate(customer_from = as.character(customer_from),
#          customer_to = as.character(customer_to))

gran_cat_dist_from <- data_validation_cat %>% 
  mutate(customer_from = as.character(customer_from),
         customer_to = as.character(customer_to)) %>% 
  left_join(cluster_result, by = c("customer_from" = "customer_id")) %>% 
  rename("group_from" = "group") %>% 
  left_join(cluster_result, by = c("customer_to" = "customer_id")) %>%  
  rename("group_to" = "group") %>% 
  group_by(gran,
           category,
           group_from, 
           group_to) %>% 
  summarise(sum = sum(distance)) %>% 
  pivot_wider(names_from = group_to, values_from = sum) %>% 
  mutate(distance = sum(`1`, `2`, `3`, `4`, `5`,`6`, `7`, `8`, `9`, `10`, `11`, `12`, `13`, `14`, `15`, `16`, `17`)) %>% 
  select(-(4:8)) %>% 
  arrange(-distance) %>% 
    rename("group"="group_from")

gran_cat_dist_to <- data_validation_cat %>% 
  mutate(customer_from = as.character(customer_from),
         customer_to = as.character(customer_to)) %>% 
  left_join(cluster_result, by = c("customer_from" = "customer_id")) %>% 
  rename("group_from" = "group") %>% 
  left_join(cluster_result, by = c("customer_to" = "customer_id")) %>%  
  rename("group_to" = "group") %>% 
  group_by(gran,
           category,
           group_from, 
           group_to) %>% 
  summarise(sum = sum(distance)) %>% 
  pivot_wider(names_from = group_from, values_from = sum) %>% 
  mutate(distance = sum(`1`, `2`, `3`, `4`, `5`,`6`, `7`, `8`, `9`, `10`, `11`, `12`, `13`, `14`, `15`, `16`, `17`)) %>% 
  select(-(4:8)) %>% 
  arrange(-distance) %>% 
    rename("group"="group_to")

# Contribution of individual category for hod

gran_cat_hod <-   gran_cat_dist %>% 
  filter(gran=="hod") %>% 
  mutate(category = as.integer(category)) %>% 
  arrange(group_from, category)

gran_cat_hod$category <- factor(gran_cat_hod$category, levels = 0:23)

# for each group, percent contribution of hours

group_total <- gran_cat_hod %>% 
  ungroup() %>% 
  group_by(group_from) %>% 
  summarise(group_total = sum(distance))

data_pcp <- gran_cat_hod %>% 
  ungroup %>% 
  left_join(group_total, by = "group_from") %>% 
  mutate(cat_contibution = distance*100/group_total) %>% 
  group_by(group_from) %>% 
  #arrange(-distance) %>% 
  select(group_from, category, cat_contibution) %>% 
  pivot_wider(names_from = "category", 
              values_from = "cat_contibution") %>% mutate(group_from = as.factor(group_from))

parcoord <- GGally::ggparcoord(data_pcp ,
                               columns = 2:ncol(data_pcp),
                               groupColumn = "group_from",
                               showPoints = TRUE, 
                               alphaLines = 1,
                               scale = "globalminmax"
) + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 10)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")+
  scale_color_manual(values=as.vector(polychrome(20)))+
  theme_bw()
parcoord 
```

# contribution of moy

```{r contribution-moy}

gran_cat_hod <-   gran_cat_dist %>% 
  filter(gran == "moy") %>% 
  #mutate(category = as.integer(category)) %>% 
  arrange(group_from, category)

# gran_cat_hod$category <- factor(gran_cat_hod$category, levels = 0:23)

gran_cat_hod$category <- factor(gran_cat_hod$category, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

# for each group, percent contribution of hours

group_total <- gran_cat_hod %>% 
  arrange(category) %>% 
  ungroup() %>% 
  group_by(group_from) %>% 
  summarise(group_total = sum(distance))

data_pcp <- gran_cat_hod %>% 
  arrange(category) %>% 
  ungroup %>% 
  left_join(group_total, by = "group_from") %>% 
  mutate(cat_contibution = distance*100/group_total) %>% 
  group_by(group_from) %>% 
  #arrange(-distance) %>% 
  select(group_from, category, cat_contibution) %>% 
  pivot_wider(names_from = "category", 
              values_from = "cat_contibution") %>% mutate(group_from = as.factor(group_from))

parcoord <- GGally::ggparcoord(data_pcp ,
                               columns = 2:ncol(data_pcp),
                               groupColumn = "group_from",
                               showPoints = TRUE, 
                               alphaLines = 1,
                               scale = "globalminmax"
) + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 10)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")+
  scale_color_manual(values=as.vector(polychrome(20)))+
  theme_bw()
parcoord 
```

>>>>

\noindent The data set contains 13,735 customers, of which 8,685 have no missing values and the remaining $5,050 customers have at least one missing value. We wanted to see if there was any structure to these missing observations, so we plotted them over time in Figure \ref{fig:missing-data}. Each row represents a customer, with the blank indicating non-missing values and the shapes indicating missing values. Figure 9 of @wang2019tsibble inspired this plot. For the most part, it appears that data for September and October 2012 are missing. Otherwise, missingness can occur at any time and there is no pattern.

```{r missing-data}
knitr::include_graphics("figs/missing-data-5050.png")
```

@@

group <- f %>% hclust (method = "ward.D") %>% cutree(k=17)

cluster_result <- bind_cols(customer_id = id, group = group) %>%
  arrange(group) %>% 
  mutate(divide_cust = c(rep(1, 177), rep(2, 176)))

@@
